Hypercoercions and a Framework for Equivalence of Cast Calculi

### 2019-10-24 paper.tex
typo

% URLs
\newcommand{\urlLazyDProof}{
	\url{https://github.com/LuKC1024/Blame-and-Coercion-Together-Again-for-the-Second-Time/tree/master/Proof}
}

@@

The reflexive transitive closure of reduction ($\judgeCreduceTrans{s}{s}$) and 
evaluation ($eval_\mathcal{C}(e)$)
are standard~\citep{felleisen03:_pllc}.

>>>>

% URLs
\newcommand{\urlLazyDProof}{
	\url{https://github.com/LuKC1024/hypercoercion-and-framework-wgt2020/tree/master/Proof}
}

@@

The reflexive transitive closure of reduction ($\judgeCreduceTrans{s}{s}$) and 
evaluation ($eval_\mathcal{x}(e)$)
are standard~\citep{felleisen03:_pllc}.
